Efficient and Effective Metric Space Indexing for Complete Record Linkage

### 2017-11-20 paper.tex
Update on Overleaf.

Locality sensitive hashing (LSH), originally proposed to allow
efficient nearest-neighbor search in high-dimensional
spaces~\cite{Ind98}, has been employed in record linkage as an indexing
technique where attribute values are hashed multiple times, and
blocks are created from those records that share some hash values.
\emph{HARRA} [CITATION?] is a record linkage approach based on Min-hash
[CITATION?] and LSH
which blocks, compares, and then merges linked records in an iterative
fashion, where merged records are re-hashed to improve overall linkage
quality. Steorts et al.~\cite{Steorts2014} recently evaluated two LSH
variations, with their main conclusion being that in order to get good
results LSH methods must be tuned to the particular datasets being
linked. This requires good quality ground truth data which may be
unavailable or very expensive to obtain.

@@

\cite{Yu2016} surveys the use of string similarity in record linkage.
Algorithms used to compare two records are characterised as being
character-based or token-based. The first category, including approaches
such as Levenshtein~\cite{Levenshtein66}, uses character differences in
the strings being compared. The second, including techniques such as
Jaccard similarity, treats records as sets of tokens, and utilises set
similarity. There are also hybrids of the two approaches.
% Do we need the rest of this paragraph?
\cite{Yu2016} categorises linkage algorithms as being based on filtering,
verification, or thresholds.
% This is missing some context as to what is going on.
Filtering algorithms generate signatures for each record, construct
inverted lists containing records with common signatures, and prune
records with no common signatures.
% Distance of prefix to what? What is the data in this context?
Verification algorithms calculate the exact distances of a prefix of the
data, and use another technique to estimate the edit distance between
records. If the estimated distance is larger than the desired similarity
threshold, the candidate may be discarded.
% This seems a bit throw-away.
Threshold-based algorithms include M-trees, Trie-Join, Pass-Join and
Partenum.

\cite{Li2006} describes a method of performing linkage using R-trees~\cite{Hjaltason1998} that fall into the threshold based category of Yu et al. Their approach demonstrated that high precision and recall may be achieved by measuring Jaccard similarity over selected fields from set of records being compared. In their evaluation, their approach achieved a recall of 99 percent in experiments in which conjunctions of similarities over fields were used. In a later paper \cite{Ciaccia97indexingmetric}  Ciaccia et al. demonstrate that using M-trees are almost always more efficient than R-trees and hence their use in the experiments described in this paper.

>>>>

Locality sensitive hashing (LSH), originally proposed to allow
efficient nearest-neighbor search in high-dimensional
spaces~\cite{Ind98}, has been employed in record linkage as an indexing
technique where attribute values are hashed multiple times, and
blocks are created from those records that share some hash values.
\emph{HARRA}~\cite{Kim10} is a record linkage approach based on Min-hash
[CITATION?] and LSH
which blocks, compares, and then merges linked records in an iterative
fashion, where merged records are re-hashed to improve overall linkage
quality. Steorts et al.~\cite{Steorts2014} recently evaluated two LSH
variations, with their main conclusion being that in order to get good
results LSH methods must be tuned to the particular datasets being
linked. This requires good quality ground truth data which may be
unavailable or very expensive to obtain.

@@

\cite{Yu2016} surveys the use of string similarity in record linkage.
Algorithms used to compare two records are characterised as being
character-based or token-based. The first category, including approaches
such as Levenshtein~\cite{Levenshtein66}, uses character differences in
the strings being compared. The second, including techniques such as
Jaccard similarity, treats records as sets of tokens, and utilises set
similarity. There are also hybrids of the two approaches.
% Do we need the rest of this paragraph?
\cite{Yu2016} categorises linkage algorithms as being based on filtering,
verification, or thresholds.
% This is missing some context as to what is going on.
Filtering algorithms generate signatures for each record, construct
inverted lists containing records with common signatures, and prune
records with no common signatures.
% Distance of prefix to what? What is the data in this context?
Verification algorithms calculate the exact distances of a prefix of the
data, and use another technique to estimate the edit distance between
records. If the estimated distance is larger than the desired similarity
threshold, the candidate may be discarded.
% This seems a bit throw-away.
% Also, these aren't themselves linkage algorithms are they?
Threshold-based algorithms include M-trees, Trie-Join, Pass-Join and
Partenum.

\cite{Li2006} describes a threshold-based method of performing linkage
using R-trees~\cite{Hjaltason1998}. It demonstrates that high quality
may be achieved using Jaccard similarity over selected record fields.
% Is next sentence necessary?
The approach achieved a recall of 99 percent in experiments in which
conjunctions of similarities over fields were used.
% Is this execution-time efficiency?
A later paper \cite{Ciaccia97indexingmetric} shows that M-trees are
almost always more efficient than R-trees, hence their use in the
experiments described in this paper.
